---
title: "p8105_hw5_yg2834"
author: "Yucong Gao"
date: "11/14/2021"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(rvest)
library(httr)
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

```

## Problem 1

Summary on city homicide states
```{r}
homicide = 
  read_csv("./data/homicide-data.csv") %>% 
  mutate(status = ifelse(disposition %in% c("Closed without arrest", "Open/No arrest"), "unsolved", "solved"), 
         location = str_c(city, state)) %>% 
  relocate(location) %>% 
  filter(location != "TulsaAL")

city_state = 
  homicide %>% 
  group_by(location) %>% 
  summarise(total = n(), 
            unsolved = sum(status == "unsolved"))

city_state = nest(city_state, city_state = total:unsolved)
```


Estimate Baltimore's proportion
```{r}
baltimore = 
  city_state %>% 
  filter(location == "BaltimoreMD") %>% 
  pull(city_state)

test_result = 
  prop.test(baltimore[[1]] %>% pull(unsolved), baltimore[[1]] %>% pull(total)) %>% 
  broom::tidy()

list(
  proportion = test_result %>% pull(estimate), 
  confidence_interval = str_c("(", round(test_result %>% pull(conf.low), 2), ", ", round(test_result %>% pull(conf.high), 2), ")")
)

```


Estimate proportion for each city
```{r}
prop_conf = function(x) {
  test_result = prop.test(x %>% pull(unsolved), x %>% pull(total)) %>% broom::tidy()
  tibble(
    prop = test_result %>% pull(estimate), 
    low_confint = test_result %>% pull(conf.low),  
    high_confint = test_result %>% pull(conf.high)
  )
}

city_state = 
  city_state %>% 
  mutate(summary = map(city_state, prop_conf)) %>% 
  unnest(col = summary) 

city_state %>% 
  mutate(location = fct_reorder(location, prop, min)) %>% 
  ggplot(aes(x = location, y = prop)) +
  geom_point() + 
  geom_errorbar(aes(ymin = low_confint, ymax = high_confint)) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

## Problem 2

```{r}
get_data = function(file_name) {
  read_csv(str_c("./data/data_2/", file_name))
}

participants = 
  tibble(
  files = list.files("./data/data_2")
)

participants = 
  participants %>% 
  mutate(data = map(files, get_data)) %>% 
  unnest(data) %>% 
  mutate(files = str_replace(files, ".csv", "")) %>% 
  separate(files, into = c("group", "id"), sep = '_') 

participants %>% 
  mutate(code = 1:20) %>% 
  pivot_longer(week_1:week_8, 
               names_to = "week", 
               values_to = "data") %>% 
  ggplot(aes(x = week, y = data, group = code, color = group)) +
  geom_line()

```
At the first week of the study, there is no obvious difference between observations from experimental and control group. But with the progress of the study, the observations from experimental group have increased and obviously different from the observations in control group. And observation data from control group fluctuated at their same level. 


## Probelm 3
```{r}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```

write the function to fill na values
```{r}
fill_na = function(vector) {
  if (!is.numeric(vector)) {
    vector[is.na(vector)] = "virginica"
  } 
  else if(is.numeric(vector)) {
    vector[is.na(vector)] = mean(vector, na.rm = T)
  }
  return(vector)
}

map(iris_with_missing, fill_na)
```

